Supplementary Material

### 2018-11-13 analyses/reproduce_analyses.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

---
title: "Reproducing Analyses for Phenotypic evolution is less constrained in complex
  food webs"
author: "Matthew A. Barbour"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

@@

We used graphical checks to evaluate whether our transformations of traits resulted in a multivariate normal distribution. As you can see from the multivariate qq-plot, it seems reasonable that our data approximates a multivariate normal distribution. Of course, statistical tests suggest otherwise. But as an example of how silly these tests can be, look at the distribution of gall diameter. It is the closest ecological variable I've ever seen that is normally distributed, yet a Shapiro-Wilks test says otherwise.

```{r MVN Assumption, echo=FALSE}

mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq", univariatePlot = "histogram")

# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")

mvn_assumption$univariateNormality[1, ]
```

We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larva survival.

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + #sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    #I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    #sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

biased_foodweb_df <- gall_selection.df %>%
  group_by(Foodweb, Gall_Number) %>%
  mutate(mean_survival = mean(gall_survival)) %>%
  filter(mean_survival > 0, mean_survival < 1) %>%
  ungroup()

biased_foodweb_model <- glmer(gall_survival ~ -1 + Foodweb + Foodweb:sc.Diam + (1|Genotype/Plant_Position/Gall_Number),
                              data = biased_foodweb_df,
                              family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Food-web alpha coefficients, include=FALSE}

# Adjust coefficients with chamber diameter
foodweb_adj_Diam <- as_tibble(boot_foodweb_model$t) %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])#,
         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebComplex:I(sc.Diam^2)"],
         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebSimple:I(sc.Diam^2)"],
         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

@@

# Plot mean fitness
plot_foodweb_mean_fitness <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  xlab("Food web") +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

# Tidy up estimates
tidy_foodweb_grads <- foodweb_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

@@

@@

```{r Egg vs. larval ptoid alpha coefficients, include=FALSE}

# Adjust coefficients with chamber diameter
egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])#,
         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebComplex:I(sc.Diam^2)"],
         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebSimple:I(sc.Diam^2)"],
         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
egglarval_alphas <- egglarval_adj_Diam %>%
  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_egglarval_alphas <- egglarval_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
```

@@

# Plot mean fitness
plot_egglarval_mean_fitness <- tidy_egglarval_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)

@@

# Tidy up estimates
tidy_egglarval_grads <- egglarval_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

@@

>>>>

---
title: "Supplementary Material"
author: "Matthew A. Barbour"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
#output:
#  pdf_document:
#    df_print: paged
#    fig_caption: true
#    citation_package: natbib
#    includes:  
#      in_header: preamble-latex.tex
#bibliography: references_ECD_supp_mat.bib
fontsize: 12pt
---

@@

We used graphical checks to evaluate whether our transformations of trait values resulted in a multivariate normal distribution. Figure S\ref{fig:Univariate_histograms} shows that our transformations resulted in approximately normal distributions for each phenotypic trait. Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line (fig. S\ref{fig:Multivariate_QQ}), suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.

```{r Univariate_histograms, echo=FALSE, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, echo=FALSE, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

# Effect of food-web treatment on trait-fitness relationships and selection gradients

We write the model in a way the independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

visreg::visreg(linear_foodweb_model, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
```

```{r Bootstrap linear food-web model, cache=TRUE, include=FALSE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

To estimate biased selection on chamber diameter, we subset our data to only include multi-chambered galls where there was variability in larval survival. We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.

<!-- We quantified biased selection on chamber diameter in the following way. First, we focus on multi-chambered galls where there is evidence of both survival and parasitism. The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent. If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors. Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism. -->

```{r Bias in food-web model, cache=TRUE}
biased_foodweb_df <- gall_selection.df %>%
  group_by(Foodweb, Gall_Number) %>%
  mutate(mean_survival = mean(gall_survival)) %>%
  filter(mean_survival > 0, mean_survival < 1) %>%
  ungroup()

# using linear model, but I'm only interested in the chamber diameter coefficient
biased_foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + 
    Foodweb:sc.Diam + 
    (1|Genotype/Plant_Position/Gall_Number),
  data = biased_foodweb_df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

biased_foodweb_confint <- tidy(biased_foodweb_model, conf.int=TRUE) %>% filter(group=="fixed")

knitr::kable(biased_foodweb_confint)
```

```{r Food-web alpha coefficients, include=FALSE}
foodweb_bind <- bind_cols(
  as_tibble(boot_linear_foodweb_model$t),
  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
)

# Adjust coefficients with chamber diameter
foodweb_adj_Diam <- foodweb_bind %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_alphas <- foodweb_adj_Diam %>%
  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_alphas <- foodweb_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))

knitr::kable(tidy_foodweb_alphas)
```

@@

# Plot mean fitness
plot_foodweb_mean_fitness <- tidy_foodweb_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  xlab("Food web") +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)

@@

# Tidy up estimates
tidy_foodweb_grads <- foodweb_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))

knitr::kable(tidy_foodweb_grads)
```

@@

# Partitioning the contribution of egg and larval parasitoids to selection gradients

Our simple food-web treatment allows us to estimate the unique contribution of egg parasitoids to selection on *Iteomyia* traits. To estimate the unique contribution of larval parasitoids, we subset our data so that our complex food-web treatment only contained attack by larval parasitoids (and gall survival). We then fit the same models as previously, including one to estimate bias.

@@

```{r Linear egg vs. larval ptoid model, cache=TRUE}
linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
```

```{r Bootstrap linear egg vs. larval model, cache=TRUE, include=FALSE}
boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

```{r Egg vs. larval ptoid alpha coefficients, include=FALSE}
egglarval_bind <- bind_cols(
  as_tibble(boot_linear_egglarval_model$t),
  select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
)

# Adjust coefficients with chamber diameter
egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])

# Calculate differences between food-web treatments, then estimate means and confidence intervals
egglarval_alphas <- egglarval_adj_Diam %>%
  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_egglarval_alphas <- egglarval_alphas %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))

knitr::kable(tidy_egglarval_alphas)
```

@@

# Plot mean fitness
plot_egglarval_mean_fitness <- tidy_egglarval_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)

@@

# Tidy up estimates
tidy_egglarval_grads <- egglarval_grads %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))

knitr::kable(tidy_egglarval_grads)
```

@@

# Reproduce Figure 2 of main manuscript

We combine our estimates of selection gradients for each food-web treatment as well as the contribution of larval parasitoids to selection in the complex food web.
